### 2016-07-27 syntax.tex
cheers

\heading{Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.  Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
\begin{definition} \rm
Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\Sigma$ is the \emph{representation alphabet}
\item $\Gamma$ is the set of possible \emph{query answers}
\item $\calS$ is a set  of multisets over universe~$\univ$
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set of supported \emph{queries}
\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$ and some \emph{auxilliary information} $\aux \in \bits^*$
\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \aux, q$, and returns \emph{answer} $a \in \Gamma$.
\end{itemize}
Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
has \emph{error-probability} $\epsilon$, if
$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$,
where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
\end{definition}

@@

\heading{Set-multiplicity Data Structures. }
Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
\end{definition}
%
%\todo{Readdress issue of representation size.  A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e. they depend on $|S|$, number of hash functions, desired error rate. }

>>>>

\heading{Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.  Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
\begin{definition}[Data Structure] \rm
Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\Sigma$ is the \emph{representation alphabet}
\item $\Gamma$ is the set of possible \emph{query answers}
\item $\calS$ is a set  of multisets over universe~$\univ$
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set of supported \emph{queries}
\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$ and some \emph{auxilliary information} $\aux \in \bits^*$
\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \aux, q$, and returns \emph{answer} $a \in \Gamma$.
\end{itemize}
\hfill\dqed
\end{definition}

\begin{definition}[Error probability and rate] \rm
Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$.
Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
has \emph{error-probability} $\epsilon$ if
$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$
where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.

Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
\hfill\dqed
\end{definition}

@@

\heading{Set-multiplicity Data Structures. }
Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
\hfill\dqed
\end{definition}
%
%\todo{Readdress issue of representation size.  A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e. they depend on $|S|$, number of hash functions, desired error rate. }
